\sysfull

### 2017-11-12 paper/coalescing.tex

>>>>

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/TskDist.pdf}
	\caption{Result of benchmark applications (Section~ref{}) task size measurement, measured in the number of instruction cycles. We observe very large variations of task sizes per each benchmark. \todo{Describe X axis, no capitals in titles - except first word; markers in addition to colors per app; remove 4.7}{Amjad}}
\label{fig:task_profiling}
\end{figure}

Result of the task size measurement is provided in Figure~\ref{fig:task_profiling}. Each benchmark was run for predefined period of time, on non-intermittent power, and at each task evocation, its execution time was measured. If a task was evoked more than once, longer execution time replaces the short one---this way we obtain conservative values of task sizes. At the end of task measurement, normalized values of task execution are assigned for each task, the shortest one being one task, the longest one X tasks.

### 2017-11-12 paper/texFigCode/alpaca-war.tex

\tikzset{
	%Define standard arrow tip
	>=stealth',
	%Define style for boxes
	punkt/.style={
		circle,
		rounded corners,
		draw=black, very thick,
		text width=2.5em,
		minimum height=1em,
		text centered},
	% Define arrow style
	pil/.style={
		->,
		thick,
		shorten <=2pt,
		shorten >=2pt,}
}

@@

	\node[punkt] (task1) {Task (1)};
	\node[punkt, below =0.7cm of task1] (task2) {Task (2)};
	\node[punkt, below =0.7cm of task2] (task3) {Task (3)};
	\node[punkt, below =0.7cm of task3] (task4) {Task (4)};

	\path[every node/.style={font=\sffamily\small}]
	(task1.west) edge [->, dotted, thick, bend right] node {Channel (1)} (task2.west)
	(task2.west) edge [->, dotted, thick, bend right] node {Channel (2)} (task3.west)
	(task3.west) edge [->, very thick, blue, bend right] node {Channel (3)} (task4.west);

	\begin{pgfonlayer}{bg}    % select the background layer
		\node[draw,thick,dotted,red,minimum width=7em, fill=blue!10, fit=(task1) (task2) (task3)] (Virtualized) {};
		\draw[<->] ([xshift=1.5cm]Virtualized.north) --node[sloped, anchor=south] {Virtualization Window} ([xshift=1.5cm]Virtualized.south);
	\end{pgfonlayer}

>>>>

\tikzset{
	%Define standard arrow tip
	>=stealth',
	%Define style for boxes
	punkt/.style={
		rectangle,
		rounded corners,
		draw=black, very thick,
		text width=4.5em,
		minimum height=1em,
		text centered},
	% Define arrow style
	pil/.style={
		->,
		thick,
		shorten <=2pt,
		shorten >=2pt,}
}

@@

	\node[punkt] (task1) {y = x+1};
	\node[below = 0.1cm of task1] (t1) {Task 1};
	\node[punkt, below =0.7cm of task1] (task2) {z = y+1};
	\node[below = 0.1cm of task2] (t2) {Task 2};
	\node[punkt, below =0.7cm of task2] (task3) {x = z+1};
	\node[below = 0.1cm of task3] (t3) {Task 3};
	\node[punkt, blue, dotted, right = 2cm of task2, fill=red!10] (task4) {y = \textcolor{red}{x}+1 
		\\ z = y+1 \\ \textcolor{red}{x} = z+1};
	\node[below = 0.3cm of task4](t4) {Merged tasks};

	\begin{pgfonlayer}{bg}    % select the background layer
		\node[draw,thick,dotted,red,minimum width=7em, fill=blue!10, fit=(task1) (task2) (t3) ] (Virtualized) {};
		\draw[<->] ([xshift=1.5cm]Virtualized.north) --node[sloped, anchor=south] {Virtualization Window} ([xshift=1.5cm]Virtualized.south);
	\end{pgfonlayer}
